Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2018-01-10 prop_letter_ajhs.tex
From: e-prints@arxiv.org [mailto:e-prints@arxiv.org] Sent: Monday, December 25, 2017 12:54 To: Tai, Yu-Tsung <yuttai@indiana.edu> Subject: arXiv submission submit/2114094
We have received your submission to arXiv. Your temporary submission
identifier is: submit/2114094.

You may update your submission at: https://arxiv.org/submit/2114094

Your article is scheduled to be announced at Wed, 27 Dec 2017 01:00:00
GMT.
The abstract will appear in the subsequent mailing as displayed below,
except that the submission identifier will be replaced by the official
arXiv identifier. Updates before Tue, 26

\documentclass[english,reprint, aps, prl,superscriptaddress, showpacs,
showkeys, longbibliography, amsmath, amssymb, floatfix]{revtex4-1}

@@

In this investigation, we explore the implications of extending
conventional quantum-mechanical probability measures to include the
effect of imperfect measurements. 
There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome of
a theory that is contextual depends upon whether compatible sets of
observables are measured together or separately; a non-contextual
theory gives the same results in either case.  A classic example of
the varying opinions on the impact of imprecision is the disagreement
between Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999}
on whether finite-precision measurements invalidate the spirit of the
Kochen-Specker
theorem~\cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}.
The Kochen-Specker theorem is in essence a mathematical statement
about contextuality, asserting that in a Hilbert space of dimension
$d \ge 3$, it is impossible to associate determinate probabilities,
$\mu(P_i)= 0$ or $1$, with every projection operator~$P_i$, in such a
way that, if a set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
$\sum_i \mu(P_i) = 1$.  Meyer showed that one {\it can\/} assign
determinate probabilities $0$ or~$1$ to the measurement outcomes when
the Hilbert space is defined over the field of rational numbers,
therefore nullifying the theorem~\citep{PhysRevLett.83.3751}.
However, Mermin then argued that measurement outcomes must depend
smoothly on slight changes in the experimental configuration, leading
him to assert that the impact of Meyer's negative result is
``unsupportable'' on physical grounds~\citep{Mermin1999}.  The debate
on whether contextuality is consistent with experimental outcomes
continues to be an active topic of
research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

@@

We also investigate the second key aspect of imprecise quantum
measurement, which is its statistical nature as reflected in the
application of the Born rule determining the probability of a given
measurement outcome~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
Here, Gleason's theorem establishes that there is no alternative to
the Born rule by demonstrating, using reasonable continuity arguments
in Hilbert spaces of dimension $d\ge3$, the existence of a unique
state $\rho$ consistent with the statistical predictions computed from
the Born rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
Our question then concerns what happens when infinite precision cannot
be achieved.  We are able to show that, while a QIVPM incorporating
the effects of finite precision might not be consistent with Gleason's
unique state~$\rho$ on all projectors defined on a Hilbert
space~$\Hilb$ of dimension $d\ge3$, there is a mathematically precise
sense in which one recovers the original Gleason theorem
asymptotically.  Specifically, it is possible to construct a class of
QIVPMs representing bounded resources that is parameterized by the
size of the intervals. We then demonstrate that all QIVPMs in this
class are consistent with a non-empty ``ball'' of quantum states whose
radius is defined by the maximal length of the intervals
characterizing the uncertainties. As the size of the intervals goes to
zero, this ball of quantum states converges to a point representing
the unique state consistent with the Born rule and Gleason's theorem.

@@

A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current pure normalized quantum
state $\ket{\phi} \in {\cal H}$; then the Born rule induces a
probability measure $\muB_{\phi}$ defined as
$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. For mixed states
$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where
$\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and $\sum_{j=1}^{N}q_{j}=1$,
the generalized Born rule induces a probability measure $\muB_{\rho}$
defined as
$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) = \sum_{j=1}^{N}
q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single \emph{real number} to an \emph{interval}~$[\ell,r]$,
where~$\ell$ intuitively corresponds to the strength of evidence for
the event~$E$ and~$1-r$ corresponds to the strength of evidence
against the same event. Under some additional assumptions, this
interval could be interpreted as the Gaussian width of a probability
distribution.

@@

Our definition of QIVPMs is consistent with classical IVPMs in the
sense that a restriction of QIVPMs to mutually commuting events,
$\eventsC$, recovers the definition of classical
IVPMs~\cite{JamisonLodwick2004}. The proof of this fact is included in the
forthcoming thesis by the first author~\citep{TaiThesis2018}. A
consequence of this fact is that known properties of classical IVPMs
directly hold for QIVPMs when one restricts to mutually commuting
events, $\eventsC$. In particular, in the classical world, it is
\emph{impossible} for experiments to result in probabilities that are
inconsistent with \emph{some} state of the system under consideration,
i.e., all IVPMs must have a non-empty ``core''~\footnote{A result by
  Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016}
  proves that a classical IVPM always contains at least one state that
  is consistent with every event.}. Interestingly, as we show in
Sec.~\ref{sec:Gleason}, it is possible in the quantum world for the
probabilities associated with some events to be inconsistent with
\emph{any} quantum state, i.e., for the QIVPM to have an empty core;
in that case, one cannot guarantee non-empty cores for finite-precision
attempts at proving Gleason's theorem by extending the Born measure
$\muB_{\rho}\left(P\right)$ to QIVPMs
$\bar{\mu}\left(P\right)$. However, if the set of events is mutually
commuting, the situation reverts to the classical case in which
probabilities always determine at least one state.

We now give the necessary technical definitions to prove this
non-empty core property. We say a QIVPM $\bar{\mu}$ is
\emph{consistent} with a state $\rho$ and a projector~$P$ if the
interval $\bar{\mu}(P)$ contains the exact probability calculated by
the Born rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}, i.e.,
  \begin{equation}
  \muB_{\rho}\left(P\right) = \Tr\left(\rho
  P\right)\in\bar{\mu}\left(P\right)\ .
  \end{equation}
In contrast with classical probability spaces, there is \emph{no
guarantee} that there exists a unique state $\rho$ consistent with a QIVPM.

@@

The proof, detailed in the forthcoming thesis~\citep{TaiThesis2018}, proceeds as
follows. From a subspace $\eventsC$ of mutually commuting events, one
can construct a partial orthonormal basis by diagonalization, and
complete this to a full orthonormal basis $\overline{\eventsC}$.  We
can then build a bijection between the QIVPM on the set of projectors
associated with this basis and the set of classical events
corresponding to this basis.  Using this correspondence together with
the classical result by
Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
we can establish that for the special case of commuting events, a
QIVPM will always have a non-empty core.

@@

\noindent Intuitively the expectation value of an observable relative
to a QIVPM $\bar{\mu}$ lies between two possible outcomes, which
themselves lie between the minimum and maximum bounds of the
probability intervals associated with each state~$\rho$ that is
consistent with~$\bar{\mu}$ on every projector in the spectral
decomposition of the observable. If $\bar{\mu}$ is a conventional
(Born) probability measure induced by a state $\rho$, then the Born
rule probability induced by every state in
$\coreBorn\left(\bar{\mu},\events'\right)$ will be
$\muB_{\rho}$ and the interval collapses to a point, thus
reducing the definition to that of
Eq.~(\ref{eq:quantum-expectation})~\citep{TaiThesis2018}.
% For example, we can extend one of the fragments of valid probability
% measures~$\mu_{1}$ defined in Table~\ref{tab:quantum-probability-measure}
% to a QIVPM~$\bar{\mu}_{3}$:
% \begin{equation}
% \begin{aligned}\bar{\mu}_{3}(\proj{0}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] & \bar{\mu}_{3}(\proj{2}) & =\left[0,0\right]\\
% \bar{\mu}_{3}(\proj{1}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] &  & \ldots\textrm{ etc.}
% \end{aligned}
% \label{eq:Born-QIVPM}
% \end{equation}
% For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
% the only state~$\rho$ consistent with $\bar{\mu}_{3}$ on $\proj{0}$,
% $\proj{1}$, and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\muB_{\proj{\ps}}$.
% Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
% which is an interval, but not between $0$ and $1$ because it is
% not a probability of an event. 
We also note that, when restricted to commuting projectors,
Eq.~(\ref{eq:quantum-interval-expectation-core}) is consistent with
the classical notion of the \emph{Choquet
  integral}~\citep{Choquet1954,GilboaSchmeidler1994,Grabisch2016}
which is used to calculate the expectation value of random variables
as a weighted average~\citep{TaiThesis2018}.

@@

Our generalization of quantum probability measures to QIVPMs allows us
to strengthen the scope of one of the fundamental theorems of quantum
physics: the Kochen-Specker
theorem~\cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}. Our
finite-precision extension of that theorem will suggest a resolution
to the debate initiated by Meyer and Mermin on the relevance of the
Kochen-Specker to experimental, and hence finite-precision, quantum
measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
Specifically, the original Kochen-Specker theorem is formulated using
a model quantum mechanical system that has \emph{definite values at
  all times}~\cite{Held2016}, i.e., its observables have infinitely
precise values at all times. Our interval-valued probability framework
will allow us to state, and prove, a stronger version of the theorem
that holds even if the observables have values that are only definite
up to some precision specified by a parameter $\delta$. Our approach
provides a quantitative realization of Mermin's
intuition~\citep{Mermin1999}:
\begin{quote}
  \ldots although the outcomes deduced from such imperfect
  measurements will occasionally differ dramatically from those
  allowed in the ideal case, if the misalignment is very slight, the
  statistical distribution of outcomes will differ only slightly from
  the ideal case.
\end{quote}

@@

\noindent The observables are constructed using the Pauli matrices
$\left\{ \mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ whose
eigenvalues are all either~$1$ or $-1$
\cite{Redhead1987-REDINA,544199,Griffiths2003,Jaeger2007,Mermin2007}.
They are arranged such that in
each row and column, \emph{except the column $j=2$}, every observable
is the product of the other two. In the $j=2$ column, we have instead
that
$\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$. Now
assume a 0-deterministic QIVPM~${\bar{\mu}}$; the expectation values
of the observables in each row relative to this 0-deterministic QIVPM
are fully determinate and must lie in either the interval $[1,1]$ or
the interval $[-1,-1]$ depending on which eigenvalue is the one whose
associated projector is certain. Since the product of any two
observables in a row is equal to the third, there must be an even
number of occurrences of the interval $[-1,-1]$ in each row and hence
in the entire table~\citep{TaiThesis2018}. However, looking at the expectation values of the
observables in each column, there must be an even number of
occurrences of the interval $[-1,-1]$ in the first two columns and an
odd number in the $j=2$ column and hence in the entire table~\citep{TaiThesis2018}. The
contradiction implies the non-existence of the assumed 0-deterministic
QIVPM. 
%% We therefore prove a stronger statement of contextuality that 
%% includes the effects of finite-precision.

>>>>

\documentclass[english,reprint, aps, prl,superscriptaddress, showpacs,
showkeys, longbibliography, amsmath, amssymb, floatfix]{revtex4-1} 
\pdfoutput=1

@@

In this investigation, we explore the implications of extending
conventional quantum-mechanical probability measures to include the
effect of imperfect measurements. 
There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome of
a theory that is contextual depends upon whether compatible sets of
observables are measured together or separately; a non-contextual
theory gives the same results in either case.  A classic example of
the varying opinions on the impact of imprecision is the disagreement
between Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999}
on whether finite-precision measurements invalidate the spirit of the
Kochen-Specker
theorem~\cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}.
The Kochen-Specker theorem is in essence a mathematical statement
about contextuality, asserting that in a Hilbert space of dimension
$d \ge 3$, it is impossible to associate determinate probabilities,
$\mu(P_i)= 0$ or $1$, with every projection operator~$P_i$, in such a
way that, if a set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
$\sum_i \mu(P_i) = 1$.  Meyer showed that one {\it can\/} assign
determinate probabilities $0$ or~$1$ to the measurement outcomes when
the Hilbert space is defined over the field of rational numbers,
therefore nullifying the theorem~\cite{PhysRevLett.83.3751}.
However, Mermin then argued that measurement outcomes must depend
smoothly on slight changes in the experimental configuration, leading
him to assert that the impact of Meyer's negative result is
``unsupportable'' on physical grounds~\cite{Mermin1999}.  The debate
on whether contextuality is consistent with experimental outcomes
continues to be an active topic of
research~\cite{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

@@

We also investigate the second key aspect of imprecise quantum
measurement, which is its statistical nature as reflected in the
application of the Born rule determining the probability of a given
measurement outcome~\cite{Born1983bibTeX,Mermin2007,Jaeger2007}.
Here, Gleason's theorem establishes that there is no alternative to
the Born rule by demonstrating, using reasonable continuity arguments
in Hilbert spaces of dimension $d\ge3$, the existence of a unique
state $\rho$ consistent with the statistical predictions computed from
the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
Our question then concerns what happens when infinite precision cannot
be achieved.  We are able to show that, while a QIVPM incorporating
the effects of finite precision might not be consistent with Gleason's
unique state~$\rho$ on all projectors defined on a Hilbert
space~$\Hilb$ of dimension $d\ge3$, there is a mathematically precise
sense in which one recovers the original Gleason theorem
asymptotically.  Specifically, it is possible to construct a class of
QIVPMs representing bounded resources that is parameterized by the
size of the intervals. We then demonstrate that all QIVPMs in this
class are consistent with a non-empty ``ball'' of quantum states whose
radius is defined by the maximal length of the intervals
characterizing the uncertainties. As the size of the intervals goes to
zero, this ball of quantum states converges to a point representing
the unique state consistent with the Born rule and Gleason's theorem.

@@

A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current pure normalized quantum
state $\ket{\phi} \in {\cal H}$; then the Born rule induces a
probability measure $\muB_{\phi}$ defined as
$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. For mixed states
$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where
$\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and $\sum_{j=1}^{N}q_{j}=1$,
the generalized Born rule induces a probability measure $\muB_{\rho}$
defined as
$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) = \sum_{j=1}^{N}
q_{j}\muB_{\phi_{j}}\left(P\right)$~\cite{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single \emph{real number} to an \emph{interval}~$[\ell,r]$,
where~$\ell$ intuitively corresponds to the strength of evidence for
the event~$E$ and~$1-r$ corresponds to the strength of evidence
against the same event. Under some additional assumptions, this
interval could be interpreted as the Gaussian width of a probability
distribution.

@@

Our definition of QIVPMs is consistent with classical IVPMs in the
sense that a restriction of QIVPMs to mutually commuting events,
$\eventsC$, recovers the definition of classical
IVPMs~\cite{JamisonLodwick2004}. The proof of this fact is included in the
forthcoming thesis by the first author~\cite{TaiThesis2018}. A
consequence of this fact is that known properties of classical IVPMs
directly hold for QIVPMs when one restricts to mutually commuting
events, $\eventsC$. In particular, in the classical world, it is
\emph{impossible} for experiments to result in probabilities that are
inconsistent with \emph{some} state of the system under consideration,
i.e., all IVPMs must have a non-empty ``core''~\footnote{A result by
  Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016}
  proves that a classical IVPM always contains at least one state that
  is consistent with every event.}. Interestingly, as we show in
Sec.~\ref{sec:Gleason}, it is possible in the quantum world for the
probabilities associated with some events to be inconsistent with
\emph{any} quantum state, i.e., for the QIVPM to have an empty core;
in that case, one cannot guarantee non-empty cores for finite-precision
attempts at proving Gleason's theorem by extending the Born measure
$\muB_{\rho}\left(P\right)$ to QIVPMs
$\bar{\mu}\left(P\right)$. However, if the set of events is mutually
commuting, the situation reverts to the classical case in which
probabilities always determine at least one state.

We now give the necessary technical definitions to prove this
non-empty core property. We say a QIVPM $\bar{\mu}$ is
\emph{consistent} with a state $\rho$ and a projector~$P$ if the
interval $\bar{\mu}(P)$ contains the exact probability calculated by
the Born rule~\cite{Born1983bibTeX,Mermin2007,Jaeger2007}, i.e.,
  \begin{equation}
  \muB_{\rho}\left(P\right) = \Tr\left(\rho
  P\right)\in\bar{\mu}\left(P\right)\ .
  \end{equation}
In contrast with classical probability spaces, there is \emph{no
guarantee} that there exists a unique state $\rho$ consistent with a QIVPM.

@@

The proof, detailed in the forthcoming thesis~\cite{TaiThesis2018}, proceeds as
follows. From a subspace $\eventsC$ of mutually commuting events, one
can construct a partial orthonormal basis by diagonalization, and
complete this to a full orthonormal basis $\overline{\eventsC}$.  We
can then build a bijection between the QIVPM on the set of projectors
associated with this basis and the set of classical events
corresponding to this basis.  Using this correspondence together with
the classical result by
Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
we can establish that for the special case of commuting events, a
QIVPM will always have a non-empty core.

@@

\noindent Intuitively the expectation value of an observable relative
to a QIVPM $\bar{\mu}$ lies between two possible outcomes, which
themselves lie between the minimum and maximum bounds of the
probability intervals associated with each state~$\rho$ that is
consistent with~$\bar{\mu}$ on every projector in the spectral
decomposition of the observable. If $\bar{\mu}$ is a conventional
(Born) probability measure induced by a state $\rho$, then the Born
rule probability induced by every state in
$\coreBorn\left(\bar{\mu},\events'\right)$ will be
$\muB_{\rho}$ and the interval collapses to a point, thus
reducing the definition to that of
Eq.~(\ref{eq:quantum-expectation})~\cite{TaiThesis2018}.
% For example, we can extend one of the fragments of valid probability
% measures~$\mu_{1}$ defined in Table~\ref{tab:quantum-probability-measure}
% to a QIVPM~$\bar{\mu}_{3}$:
% \begin{equation}
% \begin{aligned}\bar{\mu}_{3}(\proj{0}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] & \bar{\mu}_{3}(\proj{2}) & =\left[0,0\right]\\
% \bar{\mu}_{3}(\proj{1}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] &  & \ldots\textrm{ etc.}
% \end{aligned}
% \label{eq:Born-QIVPM}
% \end{equation}
% For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
% the only state~$\rho$ consistent with $\bar{\mu}_{3}$ on $\proj{0}$,
% $\proj{1}$, and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\muB_{\proj{\ps}}$.
% Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
% which is an interval, but not between $0$ and $1$ because it is
% not a probability of an event. 
We also note that, when restricted to commuting projectors,
Eq.~(\ref{eq:quantum-interval-expectation-core}) is consistent with
the classical notion of the \emph{Choquet
  integral}~\cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}
which is used to calculate the expectation value of random variables
as a weighted average~\cite{TaiThesis2018}.

@@

Our generalization of quantum probability measures to QIVPMs allows us
to strengthen the scope of one of the fundamental theorems of quantum
physics: the Kochen-Specker
theorem~\cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}. Our
finite-precision extension of that theorem will suggest a resolution
to the debate initiated by Meyer and Mermin on the relevance of the
Kochen-Specker to experimental, and hence finite-precision, quantum
measurements~\cite{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
Specifically, the original Kochen-Specker theorem is formulated using
a model quantum mechanical system that has \emph{definite values at
  all times}~\cite{Held2016}, i.e., its observables have infinitely
precise values at all times. Our interval-valued probability framework
will allow us to state, and prove, a stronger version of the theorem
that holds even if the observables have values that are only definite
up to some precision specified by a parameter $\delta$. Our approach
provides a quantitative realization of Mermin's
intuition~\cite{Mermin1999}:
\begin{quote}
  \ldots although the outcomes deduced from such imperfect
  measurements will occasionally differ dramatically from those
  allowed in the ideal case, if the misalignment is very slight, the
  statistical distribution of outcomes will differ only slightly from
  the ideal case.
\end{quote}

@@

\noindent The observables are constructed using the Pauli matrices
$\left\{ \mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ whose
eigenvalues are all either~$1$ or $-1$
\cite{Redhead1987-REDINA,544199,Griffiths2003,Jaeger2007,Mermin2007}.
They are arranged such that in
each row and column, \emph{except the column $j=2$}, every observable
is the product of the other two. In the $j=2$ column, we have instead
that
$\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$. Now
assume a 0-deterministic QIVPM~${\bar{\mu}}$; the expectation values
of the observables in each row relative to this 0-deterministic QIVPM
are fully determinate and must lie in either the interval $[1,1]$ or
the interval $[-1,-1]$ depending on which eigenvalue is the one whose
associated projector is certain. Since the product of any two
observables in a row is equal to the third, there must be an even
number of occurrences of the interval $[-1,-1]$ in each row and hence
in the entire table~\cite{TaiThesis2018}. However, looking at the expectation values of the
observables in each column, there must be an even number of
occurrences of the interval $[-1,-1]$ in the first two columns and an
odd number in the $j=2$ column and hence in the entire table~\cite{TaiThesis2018}. The
contradiction implies the non-existence of the assumed 0-deterministic
QIVPM. 
%% We therefore prove a stronger statement of contextuality that 
%% includes the effects of finite-precision.

% \begin{table*}
% \caption{\label{tab:Mermin-Peres-Computation}Compute the expectation value
% of of observables~$\ensuremath{\mathbb{1}\otimes\sigma_{z}}$, $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$,
% and $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$ relative to a 0-deterministic
% QIVPM~$\bar{\mu}$. During the computation, whenever $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$,
% $\muB_{\rho}\left(P_{1}\right)$ and $\muB_{\rho}\left(P_{2}\right)$
% must be the value list in the table. Therefore, $\expval{\mathbf{O}}_{\bar{\mu}}$
% is a singleton set.}
% \begin{tabular}{|c|c|c|c|c|c|c|c|}
% \hline 
% Observable~$\mathbf{O}$ & Spectral Decomposition~$1\cdot P_{1}-1\cdot P_{2}$ & $\bar{\mu}\left(P_{1}\right)$ & $\bar{\mu}\left(P_{2}\right)$ & $\muB_{\rho}\left(P_{1}\right)$ & $\muB_{\rho}\left(P_{2}\right)$ & $\expval{\mathbf{O}}_{\muB_{\rho}}$ & $\expval{\mathbf{O}}_{\bar{\mu}}$\tabularnewline
% \hline 
% \hline 
% $\ensuremath{\mathbb{1}\otimes\sigma_{z}}$ & $1\cdot\left(\proj{0}+\proj{2}\right)-1\cdot\left(\proj{1}+\proj{3}\right)$ & $\imposs$ & $\necess$ & $0$ & $1$ & $1\cdot0-1\cdot1=-1$ & $\left\{ -1\right\} $\tabularnewline
% \hline 
% $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$ & $1\cdot\left(\proj{0}+\proj{1}\right)-1\cdot\left(\proj{2}+\proj{3}\right)$ & $\necess$ & $\imposs$ & $1$ & $0$ & $1\cdot1-1\cdot0=1$ & $\left\{ 1\right\} $\tabularnewline
% \hline 
% $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$ & $1\cdot\left(\proj{0}+\proj{3}\right)-1\cdot\left(\proj{1}+\proj{2}\right)$ & $\imposs$ & $\necess$ & $0$ & $1$ & $1\cdot0-1\cdot1=-1$ & $\left\{ -1\right\} $\tabularnewline
% \hline 
% \end{tabular}
% \end{table*}
% \yutsung{In order to understand the expectation value of observables~$\ensuremath{\mathbb{1}\otimes\sigma_{z}}$,
% $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$, and $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$
% relative to a 0-deterministic QIVPM~$\bar{\mu}$, we first diagonalize
% these observables by the computational basis~$\Omega=\left\{ \ket{0},\ket{1},\ket{2},\ket{3}\right\} $,
% where $\ket{0}=\ket{0}\otimes\ket{0}$, $\ket{1}=\ket{0}\otimes\ket{1}$,
% $\ket{2}=\ket{1}\otimes\ket{0}$, and $\ket{3}=\ket{1}\otimes\ket{1}$.
% Since $\bar{\mu}$ is 0-deterministic, there is a unique $\ket{k_{0}}\in\Omega$
% such that $\bar{\mu}\left(\proj{k_{0}}\right)=\necess$ and $\bar{\mu}\left(\proj{k}\right)=\imposs$
% for $k\ne k_{0}$~\cite{TaiThesis2018}. Without loss of generality,
% assume $k_{0}=1$, the expectation values can be computed step-by-step
% in Table~\ref{tab:Mermin-Peres-Computation}. They are singleton
% sets whose only element is the eigenvalue of the observable. By adopting
% an intuitive product rule~$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $
% for singleton sets, these expectation values also satisfy the property~$\expval{\ensuremath{\mathbb{1}\otimes\sigma_{z}}}_{\bar{\mu}}\cdot\expval{\ensuremath{\sigma_{z}\otimes\mathbb{1}}}_{\bar{\mu}}=\expval{\ensuremath{\sigma_{z}\otimes\sigma_{z}}}_{\bar{\mu}}$
% since $\left(\ensuremath{\mathbb{1}\otimes\sigma_{z}}\right)\cdot\left(\ensuremath{\sigma_{z}\otimes\mathbb{1}}\right)=\left(\ensuremath{\sigma_{z}\otimes\sigma_{z}}\right)$.}

% A 0-deterministic QIVPM~$\bar{\mu}$ has an important property
% regarding to the expectation values of a family of $M$ commuting
% observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$ relative to
% $\bar{\mu}$. Since $\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$
% commutes, they can be diagonalized by a common orthonormal
% basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.  Since
% $\bar{\mu}$ is 0-deterministic, a unique $\ket{k_{0}}$ and a unique
% quantum probability measure~$\mu$ exists such that
% $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $ and
% $\mu\left(P\right)\in\left\{ 0,1\right\} $ for all $P\in\events$;
% $\mu\left(\proj{k}\right)=1$ if and only if
% $k=k_{0}$~\cite{TaiThesis2018}.  If we denote the product
% observables~$\prod_{j=1}^{M}\mathbf{O}_{j}$ as
% $\overline{\mathbf{O}}$, the expectation values of the
% observables~$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$ and
% $\expval{\overline{\mathbf{O}}}_{\bar{\mu}}$ are equal to the
% singleton sets whose only elements are $\expval{\mathbf{O}_{j}}_{\mu}$
% and $\expval{\overline{\mathbf{O}}}_{\mu}$, respectively. Both
% $\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\mu}$ and
% $\expval{\overline{\mathbf{O}}}_{\mu}$ are equal to the product of the
% eigenvalues corresponding to the pure state~$\ket{k_{0}}$ for each
% observable~$\mathbf{O}_{j}$. By adopting an intuitive product
% rule~$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{
%   x_{0}x_{1}\right\} $, we have the following property:
% \begin{equation}
% \prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbF{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
% \end{equation}
